Estimation of flow trajectories in a multi-lines transportation network

### 2023-02-16 latex_files/applied_network_science_article/article_v0.tex
short dataset description

\subsection{Real Data}

>>>>

\subsection{Real Data}
\subsubsection{Data set construction}
The original dataset used in this contribution consists of over 13 million rows of data over more than 1200 stop on 35 bus lines. Each data row represents a stop by a bus to embark and disembark passengers. The dataset used for further analysis is summed by stop over the year 2019.
